%%%%%%%%%%%%%%%%%
% This CV is based on the CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com), forked by Nicolás Omar González Passerino (nicolas.passerino@gmail.com) (v1.7.1b, 11 Jan 2024)
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

%% Fork (before v1.6.5a): CV dark mode toggle enabler to use a inverted color palette.
%% Use the "darkmode" option if you want a color palette used to 
% \documentclass[10pt,a4paper,ragged2e,withhyper,darkmode]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

%% Fork v1.6.5c: Overwriting sloppy environment to ignore any spaces and be used to solve overlapping cvtags
\newenvironment{sloppypar*}{\sloppy\ignorespaces}{\par}

% Change the page layout if you need to
\geometry{left=1.2cm,right=1.2cm,top=1cm,bottom=1cm,columnsep=0.75cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Fork (before v1.6.5a): Change the color codes to test your personal variant on any mode
\ifdarkmode%
  \definecolor{PrimaryColor}{HTML}{C69749}
  \definecolor{SecondaryColor}{HTML}{D49B54}
  \definecolor{ThirdColor}{HTML}{1877E8}
  \definecolor{BodyColor}{HTML}{ABABAB}
  \definecolor{EmphasisColor}{HTML}{ABABAB}
  \definecolor{BackgroundColor}{HTML}{191919}
\else%
  \definecolor{PrimaryColor}{HTML}{001F5A}
  \definecolor{SecondaryColor}{HTML}{0039AC}
  \definecolor{ThirdColor}{HTML}{F3890B}
  \definecolor{BodyColor}{HTML}{666666}
  \definecolor{EmphasisColor}{HTML}{2E2E2E}
  \definecolor{BackgroundColor}{HTML}{E2E2E2}
\fi%

\colorlet{name}{PrimaryColor}
\colorlet{tagline}{SecondaryColor}
\colorlet{heading}{PrimaryColor}
\colorlet{headingrule}{ThirdColor}
\colorlet{subheading}{SecondaryColor}
\colorlet{accent}{SecondaryColor}
\colorlet{emphasis}{EmphasisColor}
\colorlet{body}{BodyColor}
\pagecolor{BackgroundColor}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small\bfseries}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
%% \addbibresource{main.bib}

%%%%%%%%%%%%%%%%%%%%%%
% PERSONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%
\name{Alexandros Antonov}
\tagline{Senior Software Engineer, Ph.D. Candidate}
\personalinfo{
  \email{aantonov@hotmail.gr}\smallskip
  \location{Athens, Greece}\\
  \linkedin{alex-antonov-96a250105}
  \github{AAlexandros}
}

%%%%%%%%%%%%%%%%%%%%%%%%%
% ABOUT ME MACRO + HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%

% User-facing About Me command
\newcommand{\aboutme}[1]{\def\aboutmetext{#1}}

\makeatletter
\renewcommand{\makecvheader}{%
  \begin{paracol}{2}
    % --- LEFT COLUMN ---
    \raggedright
    {\LARGE\bfseries\color{name}\MakeUppercase{\@name}\par}
    \medskip
    {\large\color{tagline}\@tagline\par}
    \medskip
    {\small\@personalinfo\par}

    % --- RIGHT COLUMN ---
    \switchcolumn
    \raggedright
    \begin{tcolorbox}[colback=accent!5,colframe=accent!80!black,
                      boxrule=0.5pt,arc=2mm,left=2mm,right=2mm,top=1mm,bottom=1mm]
      \small \aboutmetext
    \end{tcolorbox}
  \end{paracol}
  \medskip
}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\aboutme{Software engineer and Ph.D. candidate with 7+ years of experience building scalable, reliable systems.
Passionate about applying research-driven innovation to deliver robust and practical solutions.}
\makecvheader
    %% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
    % \AtBeginEnvironment{itemize}{\small}
    
    %% Set the left/right column width ratio to 6:4.
    \columnratio{0.25}

    % Start a 2-column paracol. Both the left and right columns will automatically
    % break across pages if things get too long.
    \begin{paracol}{2}
        % ----- TECH STACK -----
        \cvsection{TECH STACK}
            \begin{sloppypar*}
                \cvtags{Python, Java, C\#, C++, Groovy, Bash/PowerShell}
                \medskip

                \cvtags{Flask, SQLAlchemy, Pydantic, REST APIs, Hibernate}
                \medskip

                \cvtags{PostgreSQL, MySQL, MongoDB}
                \medskip

                \cvtags{Docker, GitHub Actions CI\slash CD, Microsoft Azure, Linux, WebSphere}
                \medskip

                \cvtags{React.js, Angular, HTML, CSS, JavaScript}
                \medskip
            \end{sloppypar*}
        % ----- TECH STACK -----
        
        % ----- LEARNING -----
        \cvsection{Other Skills}
            \begin{sloppypar*}
                \cvtags{Certified Scrum Master (PSM I), Teamwork, Problem Solving, Mentoring, Presenting, Attention to Detail}
            \end{sloppypar*}
        % ----- LEARNING -----

        % ----- Languages -----
        \cvsection{Languages}
        \cvlang{English}{Proficiency Cert. (C2)}
        \cvlang{Greek}{Native Speaker}
        \cvlang{Russian}{Native Speaker}
        % ----- Languages -----

        % ----- PROJECTS -----
    \cvsection{Projects}
    \begin{itemize}[leftmargin=1em,itemsep=0.3em,topsep=0pt]
      \item \textbf{Crypto Games}\cvreference{\faGithub}{https://github.com/AAlexandros}:
            Two blockchain-based games (Solidity + React/web3.js).
      \item \textbf{Bloom Filter-Based Multicast\cvreference{\faGithub}{https://github.com/AAlexandros}}:
            Prototype ICN \emph{Publish/Subscribe} infrastructure developed as part of EU project \textbf{POINT}.
      \item \textbf{Social Network Recommendation}:
            Dataset analysis to optimize item diffusion/recommendations.
    \end{itemize}
        % ----- PROJECTS -----
            
        % ----- REFERENCES -----
        % \cvsection{References}
        %     \cvref{Prof.\ Alpha Beta}{Institute}{a.beta@university.edu}
        %     \divider

        %     \cvref{Boss\ Gamma Delta}{Business}{g.delta@business.com}
        % ----- REFERENCES -----
        
        % ----- MOST PROUD -----
        % \cvsection{Most Proud of}
        
        % \cvachievement{\faTrophy}{Fantastic Achievement}{and some details about it}\\
        % \divider
        % \cvachievement{\faHeartbeat}{Another achievement}{more details about it of course}\\
        % \divider
        % \cvachievement{\faHeartbeat}{Another achievement}{more details about it of course}
        % ----- MOST PROUD -----
        
        % \cvsection{A Day of My Life}
        
        % Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
        % \wheelchart{outer radius}{inner radius}{
        % comma-separated list of value/text width/color/detail}
        % \wheelchart{1.5cm}{0.5cm}{%
        %   6/8em/accent!30/{Sleep,\\beautiful sleep},
        %   3/8em/accent!40/Hopeful novelist by night,
        %   8/8em/accent!60/Daytime job,
        %   2/10em/accent/Sports and relaxation,
        %   5/6em/accent!20/Spending time with family
        % }
        
        % use ONLY \newpage if you want to force a page break for
        % ONLY the current column
        \newpage
        
        %% Switch to the right column. This will now automatically move to the second
        %% page if the content is too long.
        \switchcolumn
        
        % ----- EXPERIENCE -----
        \cvsection{Experience}
            \cvevent{Software Engineer}{Interamerican - Digital Solutions Department}{2016--2020}{Athens, Greece}
            \begin{itemize}
                \item Developed and maintained the company’s customer-facing web portal (Java, Apache Wicket, Angular, Hibernate, Oracle), serving up to 1.5M+ insured clients.
                \item Acted as the integration bridge between the frontend portal and numerous enterprise systems (CRM, payment gateways, legacy insurance platforms, healthcare back-office), ensuring seamless data exchange and customer transactions.
                \item Designed and consumed REST APIs to enable features such as online claims submission, policy management, and digital payments, expanding customer self-service capabilities.
                \item Collaborated in a 6-person agile team (4 devs, PO, BA) and fulfilled occasional Scrum Master duties to streamline delivery.
                \item Mentored and onboarded 4 junior engineers through pair-programming, code reviews, and knowledge-sharing sessions, accelerating team ramp-up and code quality.
                \item Conducted R\&D on new technologies to align with evolving departmental needs.
            \end{itemize}

            \divider

            \cvevent{Lead Developer}{KMicro - AI GRC Platform}{2024-Present}{Costa Mesa, CA (Remote)}
            \begin{itemize}
                \item Co-led development of an AI-driven platform that generates and revises security policies, answers questionnaires, and performs compliance assessments — reducing manual research for security teams.
                \item Designed and deployed the system architecture and infrastructure (Flask backend, SQLAlchemy, Azure Infrastructure, Docker, CI/CD with GitHub Actions).
                \item Implemented Secure Controls Framework (SCF) integration, loading thousands of controls into memory for real-time mapping across NIST, ISO, and other frameworks — the core engine of the platform.
                \item Adapted and deployed a customized version of Prowler (open-source security tool) to Azure, extending functionality to meet enterprise compliance needs.
                \item Improved system performance through ORM optimizations and efficient AI logic design, reducing excessive database calls and ensuring scalability.
                \item Served as go-to technical lead, trusted to make architectural decisions and mentor teammates, while also managing DevOps deployments.
            \end{itemize}
            
        % ----- EXPERIENCE -----

        % ----- Publications -----
        \cvsection{Publications}

        \textbf{SecureCyclon: Dependable Peer Sampling}, ICDCS 2023 —
        Resilient peer-sampling mechanism (funded by \textbf{Cardano}). \\[0.5em]

        \textbf{CliqueSensus: Ephemeral Overlays for Committee-based PoS Blockchains}, Middleware 2025 —
        Efficient consensus messaging protocol (supported by \textbf{Ethereum Foundation}).
        % ----- Publications -----

        % ----- EDUCATION -----
        \cvsection{Education}

        \cveducation
          {Ph.D. Candidate in Computer Science}
          {Athens University of Economics and Business}
          {2021 -- Ongoing}
          {Athens, Greece}
          {}
          {Title: Dependable Overlays for Blockchains}

        \cveducation
          {M.Sc. in Computer Science}
          {Athens University of Economics and Business}
          {2020 -- 2021}
          {Athens, Greece}
          {9.33}
          {}

        \cveducation
          {B.Sc. in Computer Science}
          {Athens University of Economics and Business}
          {2011 -- 2016}
          {Athens, Greece}
          {7.1}
          {}
        % ----- EDUCATION -----

    \end{paracol}
\end{document}